### 2023-02-22 README.Rmd
update the readme

Using a spatstat to generate a quasi-random scheme for the snails dataset.
```{r}
suppressPackageStartupMessages(library(spatstat))
e <- ext(covariates[[1]])
W <- owin(e[1:2],e[3:4])
snails_ppp <- ppp(presences[,1],presences[,2],W)
D <- rQuasi(100000,W)
system.time(Q <- quadscheme(snails_ppp,D,method="dirichlet", exact=FALSE))
```

>>>>

Using a spatstat to generate a quasi-random scheme for the snails dataset.
```{r,warning=FALSE}
suppressPackageStartupMessages(library(spatstat))
e <- ext(covariates[[1]])
W <- owin(e[1:2],e[3:4])
snails_ppp <- ppp(presences[,1],presences[,2],W)
D <- rQuasi(100000,W)
system.time(Q <- quadscheme(snails_ppp,D,method="dirichlet", exact=FALSE))
```
